Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-01 paper/src/paper.tex
tex update

%wait mwait lpf spf sqf lqf expfact mexpfact lrf srf laf saf
\begin{enumerate}
  \item FCFS: First-Come First-Serve, which is the widely used default policy~\cite{easy}.
  \item LCFS: Last-Come First-Serve.
  \item SPF: Smallest estimated Processing time $\widetilde{p_{j}}$ First ~\cite{bfchar}.
  \item LPF: Longest estimated Processing time First.
  \item LQF: Largest resource requirement $q_j$ First.
  \item SQF: Smallest resource requirement First.
  \item LEXP: Largest Expansion Factor First~\cite{bfchar}, where the expansion
    factor is defined as follows:
  \begin{equation} \frac{start_j - r_j + \widetilde{p_j}}{\widetilde{p_j}} \end{equation}
  where $start_j$ is the starting time of job $j$.
  \item SEXP: Smallest Expansion Factor First
  \item LRF: Largest Ratio $\frac{p_j}{q_j}$ First
  \item SRF: Smallest Ratio First
  \item LAF: Largest Area $ p_j \times q_j$ First
  \item SAF: Smallest Area First
\end{enumerate}

@@

@@

We first attract the attention of the reader to Table~\ref{tab:full}

@@

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-UniLu-Ga.pdf}

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    100 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}

  \label{fig:all}
\end{figure}

@@

@@

>>>>

\begin{enumerate}
  \item FCFS: First-Come First-Serve, which is the widely used default policy~\cite{easy}.
  \item LCFS: Last-Come First-Serve.
  \item SPF: Smallest estimated Processing time $\widetilde{p_{j}}$ First ~\cite{bfchar}.
  \item LPF: Longest estimated Processing time First.
  \item LQF: Largest resource requirement $q_j$ First.
  \item SQF: Smallest resource requirement First.
  \item LEXP: Largest Expansion Factor First~\cite{bfchar}, where the expansion
    factor is defined as follows:
  \begin{equation} \frac{start_j - r_j + \widetilde{p_j}}{\widetilde{p_j}} \end{equation}
  where $start_j$ is the starting time of job $j$.
  \item SEXP: Smallest Expansion Factor First
  \item LRF: Largest Ratio $\frac{p_j}{q_j}$ First
  \item SRF: Smallest Ratio First
  \item LAF: Largest Area $ p_j \times q_j$ First
  \item SAF: Smallest Area First
\end{enumerate}

@@

  \item An additional "Random" strategy to be used as a reference point, with
    hyperparameter $ \Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$.
    This strategy corresponds to choosing $P_i$ uniformly at random in $\left\{
      P_1 , \cdots, P_{12} \right\}$ during every period $\Delta_t$.

@@

@@

We begin by attracting the attention of the reader to Table~\ref{tab:full},
which reports the average cumulative waiting time performance improvement over
EASY(FCFS,40h) of all the fixed policies defined in ~\ref{subsec:policies}. More
precisely, let us denote the resampled traces of a given workload by $T_k$,
where k is the index of the resampled trace ($1 \le k \le 100$). We also denote
the number of jobs in the resampled trace $T_k$ by $l(T_k)$. We denote by
$\bar{w}(T_k,S)$ the cumulative waiting time obtained by a simulation run for a
strategy $S$:

\begin{equation}
  \bar{w}(T_k,P) = \sum_{j=1}^{l(T_k)} \text{Wait}_j^{P}
\end{equation}

So that the values appearing in Table~\ref{tab:full} are exactly:

\begin{equation}
  \frac{\sum_{k=1}^{k=100}\bar{w}(T_k,\text{EASY}(P_i,40h))-
  \bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}{\sum_{k=1}^{k=100}\bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}
\end{equation}

Observe that \textcolor{orange}{TODO lli  p sumlip sumlip llll sumli psumlips umlip sumil ip sumplip sumsl  ipsumul   ipsumm}.

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-UniLu-Ga.pdf}
  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    100 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}
  \label{fig:all}
\end{figure}

Figure~\ref{fig:all} reports the evolution of this quantity for the UniLu-Gaia
trace, which means that it shows how the average improvement in cumulative
waiting time evolves as a function of time. In other words, this is the average
curve obtained if one were to plot the cumulative sum of job waiting times for
every resampled trace, incrementing the sum when a job finishes. Accordingly,
the final values attained by every curve correspond exactly to the values
reported in Table~\ref{tab:full}. The dashed values represent the 10th and 90th
percentile of the values.

Observe that \textcolor{orange}{TODO}

@@

Figures~\ref{fig:small} and~\ref{fig:follow} report the main experimental
result concerning the strategies proposed in this paper. These figures show the average cumulative improvement
of over EASY(FCFS,40h) of the three strategies we propose in the same format as Figure~\ref{fig:all}.
There are four strategies displayed on the graph:

\begin{itemize}
  \item Full (simulated) Feedback ($\Delta=$1 day)
  \item Noisy (simulated) Feedback ($\Delta=$1 day)
  \item Epsilon-Greedy (Bandit Feedback) ($\Delta=$1 day, $\epsilon=0.5$)
  \item Random $P \in P_i, 1 \le k \le 100$. ($\Delta=$1 day)
\end{itemize}

Observe that \textcolor{orange}{TODO lli  p sumlip sumlip llll sumli psumlips umlip sumil ip sumplip sumsl  ipsumul   ipsumm}.

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement with respect to EASY-FCFS of fixed policies.}
  \label{tab:strat}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & Random &      & Full &      & Noisy &      & Bandit &     \\
    \hline
    $\Delta$     & day    & week & day  & week & day   & week & day    & week\\
    CTC-SP2      & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    SDSC-SP2     & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    SDSC-BLUE    & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    ANL-Intrepid & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    CEA-Curie    & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    Unilu-Gaia   & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    \hline
  \end{tabular}
\end{table*}

Table~\ref{tab:strat} gives the performance of all variants for $\Delta=$ 1
day and $\Delta=$ 1 week.

Observe that \textcolor{orange}{TODO lli  p sumlip sumlip llll sumli psumlips umlip sumil ip sumplip sumsl  ipsumul   ipsumm}.

@@

Figure~\ref{fig:mosb} gives insight regarding the behavior of the
Noisy (simulated) Feedback policy. This figure reports the share of the policies chosen
by the strategy on average as a function of time. This is an area plot, which means
that the height of the colored region represents the value. Moreover, the proportion of
times each policies are chosen by the strategy is aggregated across resampled traces.

Observe that \textcolor{orange}{TODO lli  p sumlip sumlip llll sumli psumlips umlip sumil ip sumplip sumsl  ipsumul   ipsumm}.

@@

Figure~\ref{fig:mosn} is the analogue of Figure~\ref{fig:mosb}, this time for
the Epsilon-Greedy policy.

Observe that \textcolor{orange}{TODO lli  p sumlip sumlip llll sumli psumlips umlip sumil ip sumplip sumsl  ipsumul   ipsumm}.
